Imperfect slope measurements drive overestimation in standard cone model of lake depth

### 2021-08-12 README.Rmd
sync title with ms text
sync title
update title, add reproducibility section to README

**Stachelek et al. In prep**. Bathymetry data from thousands of lakes show that lake depth prediction is confounded by difficulty modeling inlake slope.

@@

>>>>

**Stachelek et al. In prep**. Imperfect slope measurements drive overestimation in standard cone model of lake depth

@@

### Reproducibility

```shell
# local
make -t data/00_hypso/hypso.csv
make -t data/00_bathy_depth/bathy_pnts.rds
make -t data/00_bathy_depth/00_bathy_depth.csv
make -t data/00_bathy_depth/bathy_geometry.csv
make -t data/00_hypso/hypso_classes.csv
make -t data/00_reservoir_classification/reservoir_classes_clean.csv
make -t data/lagosus_depth_predictors.csv
make -t data/lagosne_depth_predictors.csv
make -t data/00_geometry/nearshore.csv
```

```shell
# docker

```

### 2021-08-12 manuscript/manuscript.Rmd
stash pre dissertation edit text
name fix
update title, add reproducibility section to README

---
title: Geometric models overestimate lake depth due to imperfect slope measurement

# Use letters for affiliations
author:
  - name: Joseph Stachelek
    affiliation: a
  - name: Patrick Hanly
    affiliation: a
  - name: Patricia A. Soranno
    affiliation: a

>>>>

---
title: Imperfect slope measurements drive overestimation in standard cone model of lake depth

# Use letters for affiliations
author:
  - name: Jemma Stachelek
    affiliation: a
  - name: Patrick J. Hanly
    affiliation: a
  - name: Patricia A. Soranno
    affiliation: a
